\chapter{Conclusion}
\label{chap:conclusion}

The work described in this thesis has been concerned with the comparison of disparity algorithms.
For this purpose, evaluation methods were introduced and integrated.
As stereoscopic datasets focusing on videos are rarely spread, the used ones for the evaluation were also introduced.
Additionally, a simple stereo matcher focusing on videos was implemented and thus described.
The following sections recap this in more detail and furthermore give a future outlook.

\section{Thesis summary}

\begin{itemize}
  \item What the thesis brought with each chapter.
  \item One small paragraph regarding one disparity algorithm.
  \item One small paragraph regarding dataset of the chair.
  \item What was implemented.
  \item What the main result of the evaluation.
\end{itemize}

%todo summarize a bit

The following modules were actually implemented:

\begin{itemize}
  \item Reader for the PFM file format.
  \item Python scripts for upcoming evaluation.
  \item Shell scripts for getting the docker containers and thus the work distributed among different instances\footnote{With instances virtual machines from DigitalOcean are meant.}.
  \item Evaluation processor for
\end{itemize}

%todo add recommendations for svddd dataset

\section{Future outlook}

A few thoughts on possible future work are outlined.
The thoughts are split in low- and high-level, from a technical perspective.
Low-level items are focused towards underlying methods of disparity algorithms, whereas high-level items focus on the bigger picture and tools which may help in developing stereo matcher.

\begin{itemize}
  \item Neuronal networks \citep{olshausen1996emergence}
  \item Other matching cost calculation methods \citep{hermann2010gradient}.
  \item Focus more on how humans experience depth? \citep{deangelis1995neuronal}
\end{itemize}

\begin{itemize}
  \item Real-time availability
  \item higher resolution
  \item What's on the market, like multi-view?
  \item Provide more real-world ground truth disparity maps \citep{kondermann2015stereo, Geiger2011IV}.
\end{itemize}
