\chapter{Checklist}
\label{chap:appendix:checklist}
Use the following list to check if you have followed the hints from this document in your work.
Refer to \cref{chap:introduction} for more information on the items.

\tabulinesep=2.5mm
% tabu allows to use relative width specifier: Use X[<ratio>] to specify the width of a column. In
% this example, the table is divided into 20 parts that are spread over the three columns.
\begin{longtabu} to \textwidth {|X[1]|X[17]|X[2]|}
% Begin header on first page
\caption[Formatting checklist]{The checklist for correctly formatted and prettier documents.}
\label{tab:checklist}
\\
\hline
\endfirsthead
% End header on first page

% Begin header on consecutive pages
\caption[]{Table continued.}
\\
\hline
\endhead
% End header on consecutive pages

% Begin footer
\multicolumn{3}{c}{Table is continued on the next page.} \\
\endfoot
% End footer

% Begin footer on last page
\endlastfoot
% End footer on last page

% Begin content
1. & Check for incorrect/missing citations (\emph{[?]}) or references (\emph{??}). & \\
\hline
2. & Remove all \LaTeX{} errors and underfull/overfull boxes. & \\
\hline
3. & Make sure to use a consistent encoding for your \TeX{} files, especially for special characters (ä, ö, ü, ß, \dots). & \\
\hline
4. & Format your \textsc{Bib}\TeX{} document: Check if the information is correct and complete for each entry. Pay notice to warnings when running  the \texttt{bibtex} command.& \\
\hline
5. & Add access dates to online sources in your bibliography (see \texttt{library.bib}) or in footnotes. & \\
\hline
6. & Run a spell checker over your document (included with some \LaTeX{} editors). & \\
\hline
7. & Place figures or tables in the \TeX{} file at the end of the paragraph you are referring to them in the text (\texttt{\textbackslash{}ref}). & \\
\hline
8. & Use the correct format for quotation marks (\emph{``x''} or \emph{\glqq{}x\grqq{}}). & \\
\hline
9. & Use the correct format for separating paragraphs (one empty line). Manual line breaks (\texttt{\textbackslash{}\textbackslash}) should be avoided. & \\
\hline
10. & Use the correct form of dashes (-, --, ---). & \\
\hline
11. & Separate citations at the end of sentences/paragraphs with a small whitespace (\texttt{\~}). & \\
\hline
12. & Name sources of images/figures you did not create yourself in the description (\emph{Source: [X]}). & \\
\hline
13. & Use the short form of captions for List of Figures, Tables, etc. (\texttt{caption[<short>]\{<long>\}}). & \\
\hline
14. & If you print your work double-sided (recommended for bachelor and master thesis) remove the \texttt{oneside} option from the document class. & \\
\hline
15. & Make sure to use high-quality figures and images that are readable both in the digital and the printed version. & \\
\hline
16. & If you include the declaration of honor do not forget to sign it. & \\
\hline
% End content
\end{longtabu}